\documentclass[11pt]{article}

\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page
\parindent 0pt
\parskip 0pt

\thispagestyle{empty}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

\begin{document}

\begin{center}
	\begin{huge}
		\bf Scott Clark
	\end{huge}
	
	\large 23915 Bent Feather Road, Conifer, CO 80433 \textbullet\ 804 687 4805 \\
	\large scottclark591@gmail.com \textbullet\ www.github.com/clarkbarz \\
\end{center}

%Objective
%\begin{LARGE}
%	\bf Objective
%\end{LARGE}
%\vspace{-0.5em}
%\begin{center}
%To obtain a position at a web development company that specializes in functional and dynamic web programming in order to further my understanding of and skills for utilizing frameworks, managing databases, practicing user-friendly design, and working in a team-driven environment. 
%\end{center}

\vspace{-0.5em}
\hrule
\vspace{0.5em}

%Education
\begin{LARGE}\bf{Education}\end{LARGE} \begin{Large}
	
\end{Large}

\vspace{0.4em}

\headerrow
	{\begin{Large}The College of William \& Mary\end{Large}}
	{Williamsburg, VA}
\headerrow
	{\textit{B.A., Major of Government and Minor of Computer Science}} 
	{\textit{08/2009 - 01/2013}}
\headerrow
	{GPA in Computer Science: 3.35}
	{Overall GPA: 3.2}

\vspace{0.2em}
\hrule
\vspace{0.7em}

%Relevant Course Work
\begin{LARGE}
	\bf Course Work in Computer Science
\end{LARGE}

\vspace{-0.4em}

\begin{itemize}
	\item \begin{large}\begin{bf}Software Design\end{bf}\end{large} - Used Java, Eclipse, test-driven development, and pair-programming to build upon and add features to an advanced maze game, then ported the code to Android.
	\vspace{-0.5em}
	\item \begin{large}\begin{bf}Algorithms\end{bf}\end{large} - Explored time complexity using various searching, sorting, selection, and graph algorithms. Implemented those algorithms in C++ to test and compare runtimes.
	\vspace{-0.5em}
	\item \begin{large}\begin{bf}Database Systems\end{bf}\end{large} - Learned relational algebra, SQL, ER mapping, and normalization of databases. Utilized Python to scrape web pages for database project information.
	\vspace{-0.5em}
	\item \begin{large}\begin{bf}Web Design\end{bf}\end{large} - Used HTML, CSS, PHP, and Photoshop to design and generate multi-page web sites.
\end{itemize}

\vspace{-0.3em}

\begin{LARGE}
	\bf Other Course Work Highlights
\end{LARGE}

\vspace{-0.5em}

\begin{itemize}
	\item \begin{large}\begin{bf}Chinese Language\end{bf}\end{large} - Studied grammar, pinyin, characters, and spoken word over three years in high school and two semesters in college. Toured China, principally Beijing and Shanghai, on language-immersion and cultural program.
\end{itemize}

%Languages & Frameworks
\begin{LARGE}
	\bf Additional Knowledge
\end{LARGE}

\vspace{-0.5em}

\begin{itemize}
	\item \begin{bf}Ruby\end{bf} - Built personal static-page blog using Jekyll. (@ http://clarkbarz.github.io)
	\vspace{-0.5em}
	\item \begin{bf}Python\end{bf} - First language used to finish courses Problem Solving and Advanced Data Structures. Scraped data from my school's professor/class database using BeautifulSoup.
	\vspace{-0.5em}
	\item \begin{bf}Javascript\end{bf} - Used both Bootstrap JS and my own scripts to run client-side code within Rails web apps. Finished real-time chat tutorial using Node.js.
\end{itemize}

\vspace{-0.5em}
%Experience
\begin{LARGE}
	\bf Experience
\end{LARGE}

\vspace{0.5em}
\headerrow
	{\begin{Large}Clark Productions\end{Large}}
	{Conifer, CO}
\headerrow
	{\textit{Full Stack Developer}}
	{\textit{06/2013 - Now}}

\vspace{-0.8em}
\begin{itemize}
	\item \begin{large}\begin{bf}Jackson\end{bf}\end{large} - Currently working with client to develop an admin-operated Rails e-store from scratch for his emerging clothing company. (@ http://salty-woodland-7650.herokuapp.com)
	\vspace{-0.6em} 
	\begin{itemize}
		\item Used Bootstrap and Sass to customize the front end of the site to the client's specifications with style. 
		\vspace{-0.4em}
		\item Designed a minimal database to completely serve the needs of the site and its users.
	\end{itemize}
	\vspace{-0.8em}
	\item \begin{large}\begin{bf}Where to Watch\end{bf}\end{large} - A Rails app of my own creation intended to help users find the best place to watch TV on the internet.
	\vspace{-0.6em} 
	\begin{itemize}
		\item Scraped and manipulated tens of thousands of episode records from a television database using short Ruby scripts. 
		\item Interfaced with the API's of such sites like Netflix and Hulu to determine which application hosts specific series. 
	\end{itemize}
	\vspace{-0.8em}
	
\end{itemize}

\vspace{0.5em}

%Kinloch
\headerrow
	{\begin{Large}Kinloch Golf Club\end{Large}}
	{Manakin-Sabot, VA}
\headerrow
	{\textit{Caddie}}
	{\textit{05/2011 - 08/2011}}
	
\vspace{-0.6em}
\begin{itemize}
	\item Developed stronger business and social skills through contact with members, guests, and employees, and realized new techniques for working with those senior in both age and experience. 
\end{itemize}

\vspace{-0.3em}

%Great Seasons
\headerrow
	{\begin{Large}Great Seasons Bistro\end{Large}}
	{Midlothian, VA}
\headerrow
	{\textit{Server}}
	{\textit{05/2010 - 08/2010}}
	
\vspace{-0.6em}
\begin{itemize}
	\item Served customers expediently, built rapport with guests and staff, and practiced strict time management while also fulfilling additional duties around the restaurant.
\end{itemize}

\vspace{-0.3em}

%Relevant o
\begin{LARGE}
	\bf Other Interests
\end{LARGE}

\vspace{-0.5em}

\begin{itemize}
	\item \begin{bf}Music\end{bf} - disco / electronic / alternative / rock / !country, \begin{bf}Gaming\end{bf} - SC2 / Steam / Catan, \begin{bf}Film\end{bf} - sci-fi / comedy / score / all, \begin{bf}Outdoors\end{bf} - hiking / biking / swimming / camping, \begin{bf}Travel\end{bf} - US / National Parks / China / future, \begin{bf}News\end{bf} - tech / hacker / world / politics
\end{itemize}





\end{document}